SVG: The Paper

### 2022-04-21 Analysis/index.Rmd
Init target sel comparison

Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?

>>>>

- Do we want to simplify this model to something in which people have some mix of a (fixed) centre and corner bias?

Do participants who differ in terms of their initial target selection differ in other ways too?

```{r echo = TRUE, fig.cap = "Whether participants have a central or corner bias for the intiial target selection appears to be largely independent of their other model parameters."}
full_join(fit, filter(am, dim == "x"), by = "observer") %>%
  pivot_longer(c(pA, pS, bP, bM, accuracy), 
               names_to = "statistic", values_to = "value") %>%
  mutate(intial_sel = if_else(mean < 0, "corner", "central")) %>%
  ggplot(aes(statistic, value, fill = intial_sel)) +
  geom_boxplot(alpha = 0.5) + 
  facet_wrap(~statistic, scales = "free", nrow = 1) +
  theme(legend.position = "bottom") + 
   scale_fill_manual("intial target selection",
                     values = c(col3[2], col3[3]))
```
